title: "Nanopore QC results"
output: html_notebook
---

```{r}
library(tidyverse)
library(stringr)
```

Barcode 1:

```{r}
 
barcode_1.txt <- read.table("barcode_1_parsed.txt", sep=",", header = TRUE)

barcode_1.1 <- barcode_1.txt %>%
   separate_rows(subject.sci.names, subject.tax.ids, sep = ";") # added this to separate rows where subject.sci.names had more than one name of a species (and subsequently the subject.tax.ids also had two numbers present for these rows.)

grep(";", barcode_1.1$subject.sci.names) # tells me if any subject.sci.names still have two per row separated by ;. Should return interger(0) if the rows have been separated properly


extraction.method <- c("Fast_dna") # these two lines add a column called extraction.method that contains the method 'fast.dna' for this dataframe
barcode_1.1$extraction.method <- extraction.method


barcode_1.1$subject.tax.ids <- as.character(barcode_1.1$subject.tax.ids) # for some reason the bind_rows function below is throwing up an error that some of the subject.tax.id columns are chracters and others are integers across all the barcode text files, so setting every barcodes column to character before merging.
```

Barcode 2

```{r}
 
barcode_2.txt <- read.table("barcode_2_parsed.txt", sep=",",  header = TRUE)

barcode_2.1 <- barcode_2.txt %>% separate_rows(subject.sci.names, subject.tax.ids, sep = ";")
grep(";", barcode_2.1$subject.sci.names) 

extraction.method <- c("Mag_max")
barcode_2.1$extraction.method <- extraction.method


barcode_2.1$subject.tax.ids <- as.character(barcode_2.1$subject.tax.ids) # for some reason the bind_rows function below is throwing up an error that some of the subject.tax.id columns are chracters and others are integers across all the barcode text files, so setting every barcodes column to character before merging.

```

Barcode 3

```{r}
   
barcode_3.txt <- read.table("barcode_3_parsed.txt", sep=",",  header = TRUE)

barcode_3.1 <- barcode_3.txt %>% separate_rows(subject.sci.names, subject.tax.ids, sep = ";")
grep(";", barcode_3.1$subject.sci.names) 

extraction.method <- c("3_peaks")
barcode_3.1$extraction.method <- extraction.method


barcode_3.1$subject.tax.ids <- as.character(barcode_3.1$subject.tax.ids) # for some reason the bind_rows function below is throwing up an error that some of the subject.tax.id columns are chracters and others are integers across all the barcode text files, so setting every barcodes column to character before merging.

```

Barcode 4

```{r}

barcode_4.txt <- read.table("barcode_4_parsed.txt", sep=",",  header = TRUE)


barcode_4.1 <- barcode_4.txt %>% separate_rows(subject.sci.names, subject.tax.ids, sep = ";")
grep(";", barcode_4.1$subject.sci.names) 

extraction.method <- c("PC")
barcode_4.1$extraction.method <- extraction.method


barcode_4.1$subject.tax.ids <- as.character(barcode_4.1$subject.tax.ids) # for some reason the bind_rows function below is throwing up an error that some of the subject.tax.id columns are chracters and others are integers across all the barcode text files, so setting every barcodes column to character before merging.
```

Barcode 5

```{r}

barcode_5.txt <- read.table("barcode_5_parsed.txt", sep=",",  header = TRUE)

barcode_5.1 <- barcode_5.txt %>% separate_rows(subject.sci.names, subject.tax.ids, sep = ";")
grep(";", barcode_5.1$subject.sci.names) 

extraction.method <- c("UCP")
barcode_5.1$extraction.method <- extraction.method


barcode_5.1$subject.tax.ids <- as.character(barcode_5.1$subject.tax.ids) # for some reason the bind_rows function below is throwing up an error that some of the subject.tax.id columns are chracters and others are integers across all the barcode text files, so setting every barcodes column to character before merging.
```

Barcode 6

```{r}

barcode_6.txt <- read.table("barcode_6_parsed.txt", sep=",",  header = TRUE)

barcode_6.1 <- barcode_6.txt %>% separate_rows(subject.sci.names, subject.tax.ids, sep = ";")
grep(";", barcode_6.1$subject.sci.names) 

extraction.method <- c("Mag_Attract")
barcode_6.1$extraction.method <- extraction.method


barcode_6.1$subject.tax.ids <- as.character(barcode_6.1$subject.tax.ids) # for some reason the bind_rows function below is throwing up an error that some of the subject.tax.id columns are chracters and others are integers across all the barcode text files, so setting every barcodes column to character before merging.
```

Barcode 7

```{r}

barcode_7.txt <- read.table("barcode_7_parsed.txt", sep=",",  header = TRUE)

barcode_7.1 <- barcode_7.txt %>% separate_rows(subject.sci.names, subject.tax.ids, sep = ";")
grep(";", barcode_7.1$subject.sci.names) 

extraction.method <- c("Genomic_tip")
barcode_7.1$extraction.method <- extraction.method

barcode_7.1$subject.tax.ids <- as.character(barcode_7.1$subject.tax.ids) # for some reason the bind_rows function below is throwing up an error that some of the subject.tax.id columns are chracters and others are integers across all the barcode text files, so setting every barcodes column to character before merging.

```

Now merging all dataframes using tidyverse bind_rows

```{r}
combined_blast <- bind_rows(barcode_1.1, barcode_2.1, barcode_3.1,barcode_4.1,barcode_5.1,barcode_6.1,barcode_7.1)

```

Setting up a table with taxa info for the combined

```{r}
#install.packages("taxonomizr")
library(taxonomizr)
prepareDatabase(getAccessions = FALSE) # name is "nameNode.sqlite"
taxaID <- as.vector(combined_blast$subject.tax.ids)

taxa<-getTaxonomy(taxaID,sqlFile = "nameNode.sqlite", sep ) # Should note I always get warning messages " cannot remove file 'C:\Users\keegk\AppData\Local\Temp\RtmpoB5Zmx\file52c43a1f5e8e', reason 'Permission denied' Warning in file.remove(tmp) :" or some variation whenever I run this code 

```

 converting row names to column using rownames_to_column:
```{r}
taxa <- data.frame(taxa)
taxa1<- tibble::rownames_to_column(taxa, var = "subject.tax.ids")
taxa1
```

We need to remove all the noise around the subject.tax.ids and just keep the number 

```{r}
taxa1$subject.tax.ids <- str_extract(taxa1$subject.tax.ids, "\\d+") # regex command "\\d+") keeps only digits from 0-9
taxa1
#nrow(taxa1) #42965
taxa_table_distinct <- distinct(taxa1)
#nrow(taxa_table_distinct) #9239
```


And finally merging both taxonomy table and blast table using data.table  (left join and merge crashed my laptop!)

```{r}
library(data.table)

combined_blast_table = data.table(combined_blast_sorted , key="subject.tax.ids")
taxa_table = data.table(taxa_table_distinct , key="subject.tax.ids")

df.merged <- merge(combined_blast_table, taxa_table)
View(df.merged)
#randomly checked subject.tax.ids in this dataframe against ncbi search bar to check if the tax.id matches the species it should. checked rows 5, 82994, 349510, 549498, 572499...all match!yay!
```


*Summary Statistics*

Summarise how many superkingdoms per extraction method

```{r}

#phylum count to proportions
superkingdom_prop <- df.merged%>% 
 group_by(extraction.method, superkingdom) %>%
  summarise(superkingdom_count = n()) %>%
  mutate(prop =prop.table(superkingdom_count)) %>%
  arrange(extraction.method, desc(prop)) 
superkingdom_prop

#plot

superkingdom_plot <-ggplot(superkingdom_prop,aes(x=extraction.method,y=prop,fill=superkingdom))+geom_col(position=position_dodge())+geom_text(aes(label=sprintf("%0.2f", prop)), position=position_dodge(width=0.9), vjust=-0.25, size=3)+labs(x="DNA extraction method", y="Proportion", title="Proportional distribution of superkingdoms present per extraction method")
superkingdom_plot  +                      # Change fill & color
  scale_fill_brewer(palette = "PRGn")

```

Dataframe and barchart with proportion of bacterial phyla only
```{r}
superkingdom_bac_prop <- df.merged%>% 
 group_by(extraction.method, superkingdom, phylum) %>%
  filter(superkingdom == "Bacteria") %>%
  summarise(superkingdom_count = n()) %>%
  mutate(prop =prop.table(superkingdom_count)) %>%
  arrange(extraction.method, desc(prop)) 
superkingdom_bac_prop

superkingdom_bac_plot <-ggplot(superkingdom_bac_prop,aes(x=extraction.method,y=prop,fill=superkingdom))+geom_col(position=position_dodge())+geom_text(aes(label=sprintf("%0.2f", prop)), position=position_dodge(width=0.9), vjust=-0.25, size=3)+labs(x="DNA extraction method", y="Proportion", title="Proportional distribution of superkingdoms present per extraction method")

superkingdom_bac_plot  +                      # Change fill & color
  scale_fill_brewer(palette = "PRGn")

```


Graph of proportion of everything else (archaea, eukaryota, NA) :
```{r}
superkingdom_other_prop <- df.merged%>% 
 group_by(extraction.method, superkingdom) %>%
  filter(!str_detect(superkingdom, "Bacteria")) %>%
  summarise(superkingdom_count = n()) %>%
  mutate(prop =prop.table(superkingdom_count)) %>%
  arrange(extraction.method, desc(prop)) 
  
superkingdom_other_prop

superkingdom_other_plot <-ggplot(superkingdom_other_prop,aes(x=extraction.method,y=prop,fill=superkingdom))+geom_col(position=position_dodge())+geom_text(aes(label=sprintf("%0.2f", prop)), position=position_dodge(width=0.9), vjust=-0.25, size=3)+labs(x="DNA extraction method", y="Proportion", title="Proportional distribution of superkingdoms present per extraction method")
superkingdom_other_plot  +                      # Change fill & color
  scale_fill_brewer(palette = "PRGn")

```

Graph of *count* of everything else (archaea, eukaryota, NA) :
```{r}
superkingdom_other_count <- df.merged%>% 
 group_by(extraction.method, superkingdom) %>%
  filter(!str_detect(superkingdom, "Bacteria")) %>%
  summarise(superkingdom_count = n()) #%>%
  #mutate(prop =prop.table(superkingdom_count)) %>%
 # arrange(extraction.method, desc(prop)) 
  
superkingdom_other_prop

superkingdom_other_plot <-ggplot(superkingdom_other_count,aes(x=extraction.method,y=superkingdom_count,fill=superkingdom))+geom_col(position=position_dodge())+geom_text(aes(label=sprintf("%0.2f", superkingdom_count)), position=position_dodge(width=0.9), vjust=-0.25, size=3)+labs(x="DNA extraction method", y="Count", title="Proportional distribution of superkingdoms present per extraction method")
superkingdom_other_plot  +                      # Change fill & color
  scale_fill_brewer(palette = "PRGn")

```


What phyla are the eukaryotes made up of?

```{r}
phylum_euk_prop <- df.merged%>% 
 group_by(extraction.method, superkingdom, phylum) %>%
  filter(superkingdom == "Eukaryota") %>%
  summarise(phylum_count = n()) %>%
  mutate(prop =prop.table(phylum_count)) %>%
  arrange(extraction.method, desc(prop)) 
  
species_euk_prop

phylum_euk_plot <-ggplot(phylum_euk_prop,aes(x=extraction.method,y=prop,fill=phylum))+geom_col(position=position_dodge())+geom_text(aes(label=sprintf("%0.2f", prop)), position=position_dodge(width=0.9), vjust=-0.25, size=3)+labs(x="DNA extraction method", y="Count", title="Proportional distribution of superkingdoms present per extraction method")
phylum_euk_plot  +                      # Change fill & color
  scale_fill_brewer(palette = "PRGn")

```

What species are the chordatas made up of? What are the top 10 hits per extraction method?

```{r}
phylum_chor_prop <- df.merged%>% 
 group_by(extraction.method, phylum, species) %>%
  filter(phylum == "Chordata") %>%
  summarise(species_count = n()) %>%
  mutate(prop =prop.table(species_count)) %>%
  slice(1:10) %>%
  arrange(species, desc(prop))# %>%
  #slice(1:10) 
  
phylum_chor_prop

phylum_chor_plot <-ggplot(phylum_chor_prop,aes(x=extraction.method,y=prop,fill=species))+geom_col(position=position_dodge())+geom_text(aes(label=sprintf("%0.2f", prop)), position=position_dodge(width=0.9), vjust=-0.25, size=3)+labs(x="DNA extraction method", y="Count", title="Proportional distribution of superkingdoms present per extraction method")
phylum_chor_plot  +                      # Change fill & color
  scale_fill_brewer(palette = "PRGn")

```






Summarise how many bacterial phyla per extraction method

```{r}
#install.packages("RColorBrewer")                   # Install RColorBrewer package
library("RColorBrewer") 
#display.brewer.all(colorblindFriendly = TRUE) gives you codes for all the colour blind friendly colour templates
phyla_prop <- df.merged %>% 
  group_by(extraction.method, superkingdom, phylum) %>% 
  filter(superkingdom == "Bacteria") %>%
  summarise(phylum_count = n()) %>%
  mutate(prop =prop.table(phylum_count)) %>%
  arrange(extraction.method, desc(prop)) %>%
    slice(1:10) 
phyla_prop #pseudomonadota is a synonym for proteobacteria!Bacillota used to be called firmicutes....see https://science.thewire.in/the-sciences/ncbi-taxonomy-prokaryotes-phylum-names-firmicutes-proteobacteria/ for recent (2021) taxonomy changes
 
bacteria_plot <- ggplot(phyla_prop, aes(x=extraction.method,
                       y=prop, fill=phylum)) +
                      geom_col() +
                      labs(x="DNA extraction method", y="Proportion", title="Proportional distribution of bacterial phyla present per extraction method")
bacteria_plot +                      # Change fill & color
  scale_fill_brewer(palette = "RdYlBu") # you can choose different palettes at colourbrewer2.org and pasting the palette template from the url, after scheme = . "RdYlBu" is a colour-blind friendly palette and you can filter for this on the website.
```






