**1:Loading packages**

First, lets load in any required packages:

```{r setup}
library(tidyverse)
packageVersion("tidyverse")
#install.packages("RColorBrewer")
library(RColorBrewer)
require("knitr")
opts_knit$set(root.dir = "G:/Nanopore/SQKRBK004/Extraction_experiment_run_22.2.23/Extraction_experiment") #having to use my harddrive as project location because file sizes (the summary seq files) are too large for my OneDrive
#library(stringr)
#library(scales) #needed for label_percent function
```

\*\*111:Summary sequencing file\*

Next, lets load in the summary sequencing files for each run included in the model (3 RUNS). Note I use guupy summary seq files, not dorado, as dorado loses lots of info (no of bases, passed reads etc) that I need for the model

```{r}


run1_sequencing_summary <- read_delim("guppy_run1_sum_seq.txt")

run1_sequencing_summary<- save(run1_sequencing_summary, file = "run1_sequencing_summary")
load("run1_sequencing_summary")

run2_sequencing_summary <- read_delim("guppy_run2_sequencing_summary.txt") #run2

run2_sequencing_summary<- save(run2_sequencing_summary, file = "run2_sequencing_summary")
load("run2_sequencing_summary")



run3_sequencing_summary <- read_delim("guppy_run3_sum_seq.txt") #run3

run3_sequencing_summary<- save(run3_sequencing_summary, file = "run3_sequencing_summary")
load("run3_sequencing_summary")

#merged_summary_seq <- full_join(x =sequencing_summary, y = run111_sequencing_summary, by ="barcode") #lets not try merge the two full summary seq files, the merge is too large. instead lets get the number of reads (lines) of each barcode below as we did for the first summary seq file and then les merge this smaller dataframe...we dont need all the info int he summary seq file, just the number of reads (rows) assigned to each barcode..see line 11187 for this code



```



Now, lets filter out from these sequencing summary files, any incorrect/unclassified barcodes (barcode switching). We cant actually do this because 1) this summary sequencing file contains all the barcodes, not one, so we can't filter out any that shouldn't be there, 111) I thought maybe we can filter any barcodes that have a barcode score less than 60 (this is what happened when we filtered out incorrect barcodes from the indidivudal summary seq files in the extraction experiement run), however these summary seq files have been generated from Dorado not Guppy (guppy used to dfdemultiplex in dna extraction exp run), and the output in the sum seq file is different - there is only a barcode column, no barcode scoring column or any other barcode related column. However, what we can do is filter out unclassified reads from dorado sum seq, to get a better idea of number of reads actually being assigned to barcodes:

```{r}

#run1

run1_sequencing_summary_clean <- run1_sequencing_summary %>%
                      filter(barcode_score >= 60) %>% # #set to 60, as this was the cut-off score of barcodes kept in extraction exp summary sequencing files when we removed any incorrect barcodes or unclassififed data. Still unclassified barcodes when set to >= 60, so further remove unclassified reads:
                      filter(!barcode_arrangement == "unclassified")

##extracting reads with barcode score less than 60 and any unclassified reads,  to remove from the blast text file for this run:

run1_sequencing_summary_reads_to_remove<- run1_sequencing_summary %>% 
                      filter(!barcode_score >= 60) %>% # #set to 60, as this was the cut-off score of barcodes kept in extraction exp summary sequencing files when we removed any incorrect barcodes or unclassififed data. Still unclassified barcodes when set to >= 60, so further remove unclassified reads:
                      filter(barcode_arrangement == "unclassified") 

run1_sequencing_summary_reads_to_remove<- save(run1_sequencing_summary_reads_to_remove, file = "run1_sequencing_summary_reads_to_remove")
load("run1_sequencing_summary_reads_to_remove")


#run2
run2_sequencing_summary_clean <- run2_sequencing_summary %>%
                      filter(barcode_score >= 60) %>%
                      filter(!barcode_arrangement == "unclassified")


##extracting reads with barcode score less than 60 and any unclassified reads,  to remove from the blast text file for this run:

run2_sequencing_summary_reads_to_remove<- run2_sequencing_summary %>% 
                      filter(!barcode_score >= 60) %>% # #set to 60, as this was the cut-off score of barcodes kept in extraction exp summary sequencing files when we removed any incorrect barcodes or unclassififed data. Still unclassified barcodes when set to >= 60, so further remove unclassified reads:
                      filter(barcode_arrangement == "unclassified")

run2_sequencing_summary_reads_to_remove<- save(run2_sequencing_summary_reads_to_remove, file = "run2_sequencing_summary_reads_to_remove")
load("run2_sequencing_summary_reads_to_remove")


#run3
run3_sequencing_summary_clean <- run3_sequencing_summary%>%
                      filter(barcode_score >= 60) %>%
                      filter(!barcode_arrangement == "unclassified")


##extracting reads with barcode score less than 60 and any unclassified reads,  to remove from the blast text file for this run:

run3_sequencing_summary_reads_to_remove<- run3_sequencing_summary %>% 
                      filter(!barcode_score >= 60) %>% # #set to 60, as this was the cut-off score of barcodes kept in extraction exp summary sequencing files when we removed any incorrect barcodes or unclassififed data. Still unclassified barcodes when set to >= 60, so further remove unclassified reads:
                      filter(barcode_arrangement == "unclassified")

run3_sequencing_summary_reads_to_remove<- save(run3_sequencing_summary_reads_to_remove, file = "run3_sequencing_summary_reads_to_remove")
load("run3_sequencing_summary_reads_to_remove")



```

#How many counts of reads, no. bases and passed reads per barcode in run 1?

```{r}


#bar1

bar1 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode01")

nrow_bar1 <- nrow(bar1)

sum_bar1 <- sum(bar1$sequence_length_template)

bar1_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode01") %>%
        filter(passes_filtering == TRUE)%>%
        nrow

#bar2

bar2 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode02")

nrow_bar2 <- nrow(bar2)

sum_bar2 <- sum(bar2$sequence_length_template)

bar2_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode02") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar3

bar3 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode03")

nrow_bar3 <- nrow(bar3)

sum_bar3 <- sum(bar3$sequence_length_template)

bar3_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode03") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar4

bar4 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode04")

nrow_bar4 <- nrow(bar4)

sum_bar4 <- sum(bar4$sequence_length_template)

bar4_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode04") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar5

bar5 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode05")

nrow_bar5 <- nrow(bar5)

sum_bar5 <- sum(bar5$sequence_length_template)

bar5_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode05") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar6

bar6 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode06")

nrow_bar6 <- nrow(bar6)

sum_bar6 <- sum(bar6$sequence_length_template)

bar6_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode06") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar7

bar7 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode07")

nrow_bar7 <- nrow(bar7)

sum_bar7 <- sum(bar7$sequence_length_template)

bar7_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode07") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar8

bar8 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode08")

nrow_bar8 <- nrow(bar8)

sum_bar8 <- sum(bar8$sequence_length_template)

bar8_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode08") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar9

bar9 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode09")

nrow_bar9 <- nrow(bar9)

sum_bar9 <- sum(bar9$sequence_length_template)

bar9_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode09") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar10

bar10 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode10")

nrow_bar10 <- nrow(bar10)

sum_bar10 <- sum(bar10$sequence_length_template)

bar10_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode10") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar11

bar11 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode11")

nrow_bar11 <- nrow(bar11)

sum_bar11 <- sum(bar11$sequence_length_template)

bar11_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode11") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar12

bar12 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode12")

nrow_bar12 <- nrow(bar12)

sum_bar12 <- sum(bar12$sequence_length_template)

bar12_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode12") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar13

bar13 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode13")

nrow_bar13 <- nrow(bar13)

sum_bar13 <- sum(bar13$sequence_length_template)

bar13_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode13") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar14

bar14 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode14")

nrow_bar14 <- nrow(bar14)

sum_bar14<- sum(bar14$sequence_length_template)

bar14_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode14") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar15

bar15 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode15")

nrow_bar15 <- nrow(bar15)

sum_bar15 <- sum(bar15$sequence_length_template)

bar15_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode15") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar16

bar16 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode16")

nrow_bar16 <- nrow(bar16)

sum_bar16 <- sum(bar16$sequence_length_template)

bar16_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode16") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar17

bar17 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode17")

nrow_bar17 <- nrow(bar17)

sum_bar17 <- sum(bar17$sequence_length_template)

bar17_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode17") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar18

bar18 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode18")

nrow_bar18<- nrow(bar18)

sum_bar18 <- sum(bar18$sequence_length_template)

bar18_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode18") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar19

bar19 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode19")

nrow_bar19 <- nrow(bar19)

sum_bar19 <- sum(bar19$sequence_length_template)

bar19_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode19") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar20

bar20 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode20")

nrow_bar20 <- nrow(bar20)

sum_bar20 <- sum(bar20$sequence_length_template)

bar20_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode20") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar21

bar21 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode21")

nrow_bar21 <- nrow(bar21)

sum_bar21 <- sum(bar21$sequence_length_template)

bar21_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode21") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar22

bar22 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode22")

nrow_bar22 <- nrow(bar22)

sum_bar22 <- sum(bar22$sequence_length_template)

bar22_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode22") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar23

bar23 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode23")

nrow_bar23 <- nrow(bar23)

sum_bar23 <- sum(bar23$sequence_length_template)

bar23_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode23") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar24

bar24 <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode24")

nrow_bar24 <- nrow(bar24)

sum_bar24 <- sum(bar24$sequence_length_template)

bar24_passes <- run1_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode24") %>%
        filter(passes_filtering == TRUE) %>%
        nrow
```





```{r}
###DATFRAME run 1
#create a dataframe to store all this info:

barcode <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24)
reads <- c(nrow_bar1,nrow_bar2,nrow_bar3,nrow_bar4,nrow_bar5,nrow_bar6,nrow_bar7,nrow_bar8,nrow_bar9,nrow_bar10,nrow_bar11,nrow_bar12,nrow_bar13,nrow_bar14,nrow_bar15,nrow_bar16,nrow_bar17,nrow_bar18,nrow_bar19,nrow_bar20,nrow_bar21,nrow_bar21,nrow_bar23,nrow_bar24) #vector containing all the reads per barcode
bases <- c(sum_bar1,sum_bar2,sum_bar3,sum_bar4,sum_bar5,sum_bar6,sum_bar7,sum_bar8,sum_bar9,sum_bar10,sum_bar11,sum_bar12,sum_bar13,sum_bar14,sum_bar15,sum_bar16,sum_bar17,sum_bar18,sum_bar19,sum_bar20,sum_bar21,sum_bar21,sum_bar23,sum_bar24)#vector containing all the bases per barcode
passes <- c(bar1_passes,bar2_passes,bar3_passes,bar4_passes,bar5_passes,bar6_passes,bar7_passes,bar8_passes,bar9_passes,bar10_passes,bar11_passes,bar12_passes,bar13_passes,bar14_passes,bar15_passes,bar16_passes,bar17_passes,bar18_passes,bar19_passes,bar20_passes,bar21_passes,bar22_passes,bar23_passes,bar24_passes) #vector containing all the passed reads per barcode
run <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)

run1_metrics_for_model <- data.frame(barcode,reads,bases,passes,run)
print(run1_metrics_for_model)

write.csv(run1_metrics_for_model, "run1_metrics_for_model.csv")

```









#How many counts of reads, no. bases and passed reads per barcode in run 2?

```{r}


#bar1

bar1 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode01")

nrow_bar1 <- nrow(bar1)

sum_bar1 <- sum(bar1$sequence_length_template)

bar1_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode01") %>%
        filter(passes_filtering == TRUE)%>%
        nrow

#bar2

bar2 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode02")

nrow_bar2 <- nrow(bar2)

sum_bar2 <- sum(bar2$sequence_length_template)

bar2_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode02") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar3

bar3 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode03")

nrow_bar3 <- nrow(bar3)

sum_bar3 <- sum(bar3$sequence_length_template)

bar3_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode03") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar4

bar4 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode04")

nrow_bar4 <- nrow(bar4)

sum_bar4 <- sum(bar4$sequence_length_template)

bar4_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode04") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar5

bar5 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode05")

nrow_bar5 <- nrow(bar5)

sum_bar5 <- sum(bar5$sequence_length_template)

bar5_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode05") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar6

bar6 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode06")

nrow_bar6 <- nrow(bar6)

sum_bar6 <- sum(bar6$sequence_length_template)

bar6_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode06") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar7

bar7 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode07")

nrow_bar7 <- nrow(bar7)

sum_bar7 <- sum(bar7$sequence_length_template)

bar7_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode07") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar8

bar8 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode08")

nrow_bar8 <- nrow(bar8)

sum_bar8 <- sum(bar8$sequence_length_template)

bar8_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode08") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar9

bar9 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode09")

nrow_bar9 <- nrow(bar9)

sum_bar9 <- sum(bar9$sequence_length_template)

bar9_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode09") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar10

bar10 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode10")

nrow_bar10 <- nrow(bar10)

sum_bar10 <- sum(bar10$sequence_length_template)

bar10_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode10") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar11

bar11 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode11")

nrow_bar11 <- nrow(bar11)

sum_bar11 <- sum(bar11$sequence_length_template)

bar11_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode11") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar12

bar12 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode12")

nrow_bar12 <- nrow(bar12)

sum_bar12 <- sum(bar12$sequence_length_template)

bar12_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode12") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar13

bar13 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode13")

nrow_bar13 <- nrow(bar13)

sum_bar13 <- sum(bar13$sequence_length_template)

bar13_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode13") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar14

bar14 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode14")

nrow_bar14 <- nrow(bar14)

sum_bar14<- sum(bar14$sequence_length_template)

bar14_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode14") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar15

bar15 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode15")

nrow_bar15 <- nrow(bar15)

sum_bar15 <- sum(bar15$sequence_length_template)

bar15_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode15") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar16

bar16 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode16")

nrow_bar16 <- nrow(bar16)

sum_bar16 <- sum(bar16$sequence_length_template)

bar16_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode16") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar17

bar17 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode17")

nrow_bar17 <- nrow(bar17)

sum_bar17 <- sum(bar17$sequence_length_template)

bar17_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode17") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar18

bar18 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode18")

nrow_bar18<- nrow(bar18)

sum_bar18 <- sum(bar18$sequence_length_template)

bar18_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode18") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar19

bar19 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode19")

nrow_bar19 <- nrow(bar19)

sum_bar19 <- sum(bar19$sequence_length_template)

bar19_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode19") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar20

bar20 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode20")

nrow_bar20 <- nrow(bar20)

sum_bar20 <- sum(bar20$sequence_length_template)

bar20_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode20") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar21

bar21 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode21")

nrow_bar21 <- nrow(bar21)

sum_bar21 <- sum(bar21$sequence_length_template)

bar21_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode21") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar22

bar22 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode22")

nrow_bar22 <- nrow(bar22)

sum_bar22 <- sum(bar22$sequence_length_template)

bar22_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode22") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar23

bar23 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode23")

nrow_bar23 <- nrow(bar23)

sum_bar23 <- sum(bar23$sequence_length_template)

bar23_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode23") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar24

bar24 <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode24")

nrow_bar24 <- nrow(bar24)

sum_bar24 <- sum(bar24$sequence_length_template)

bar24_passes <- run2_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode24") %>%
        filter(passes_filtering == TRUE) %>%
        nrow


```


```{r}
###DATFRAME run 2
#create a dataframe to store all this info:

barcode <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24)
reads <- c(nrow_bar1,nrow_bar2,nrow_bar3,nrow_bar4,nrow_bar5,nrow_bar6,nrow_bar7,nrow_bar8,nrow_bar9,nrow_bar10,nrow_bar11,nrow_bar12,nrow_bar13,nrow_bar14,nrow_bar15,nrow_bar16,nrow_bar17,nrow_bar18,nrow_bar19,nrow_bar20,nrow_bar21,nrow_bar21,nrow_bar23,nrow_bar24) #vector containing all the reads per barcode
bases <- c(sum_bar1,sum_bar2,sum_bar3,sum_bar4,sum_bar5,sum_bar6,sum_bar7,sum_bar8,sum_bar9,sum_bar10,sum_bar11,sum_bar12,sum_bar13,sum_bar14,sum_bar15,sum_bar16,sum_bar17,sum_bar18,sum_bar19,sum_bar20,sum_bar21,sum_bar21,sum_bar23,sum_bar24)#vector containing all the bases per barcode
passes <- c(bar1_passes,bar2_passes,bar3_passes,bar4_passes,bar5_passes,bar6_passes,bar7_passes,bar8_passes,bar9_passes,bar10_passes,bar11_passes,bar12_passes,bar13_passes,bar14_passes,bar15_passes,bar16_passes,bar17_passes,bar18_passes,bar19_passes,bar20_passes,bar21_passes,bar22_passes,bar23_passes,bar24_passes) #vector containing all the passed reads per barcode
run <- c(2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2)

run2_metrics_for_model <- data.frame(barcode,reads,bases,passes,run)
print(run2_metrics_for_model)

write.csv(run2_metrics_for_model, "run2_metrics_for_model.csv")

```


run 3:

```{r}


#bar1

bar1 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode01")

nrow_bar1 <- nrow(bar1)

sum_bar1 <- sum(bar1$sequence_length_template)

bar1_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode01") %>%
        filter(passes_filtering == TRUE)%>%
        nrow

#bar2

bar2 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode02")

nrow_bar2 <- nrow(bar2)

sum_bar2 <- sum(bar2$sequence_length_template)

bar2_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode02") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar3

bar3 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode03")

nrow_bar3 <- nrow(bar3)

sum_bar3 <- sum(bar3$sequence_length_template)

bar3_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode03") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar4

bar4 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode04")

nrow_bar4 <- nrow(bar4)

sum_bar4 <- sum(bar4$sequence_length_template)

bar4_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode04") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar5

bar5 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode05")

nrow_bar5 <- nrow(bar5)

sum_bar5 <- sum(bar5$sequence_length_template)

bar5_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode05") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar6

bar6 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode06")

nrow_bar6 <- nrow(bar6)

sum_bar6 <- sum(bar6$sequence_length_template)

bar6_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode06") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar7

bar7 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode07")

nrow_bar7 <- nrow(bar7)

sum_bar7 <- sum(bar7$sequence_length_template)

bar7_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode07") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar8

bar8 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode08")

nrow_bar8 <- nrow(bar8)

sum_bar8 <- sum(bar8$sequence_length_template)

bar8_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode08") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar9

bar9 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode09")

nrow_bar9 <- nrow(bar9)

sum_bar9 <- sum(bar9$sequence_length_template)

bar9_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode09") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar10

bar10 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode10")

nrow_bar10 <- nrow(bar10)

sum_bar10 <- sum(bar10$sequence_length_template)

bar10_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode10") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar11

bar11 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode11")

nrow_bar11 <- nrow(bar11)

sum_bar11 <- sum(bar11$sequence_length_template)

bar11_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode11") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar12

bar12 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode12")

nrow_bar12 <- nrow(bar12)

sum_bar12 <- sum(bar12$sequence_length_template)

bar12_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode12") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar13

bar13 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode13")

nrow_bar13 <- nrow(bar13)

sum_bar13 <- sum(bar13$sequence_length_template)

bar13_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode13") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar14

bar14 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode14")

nrow_bar14 <- nrow(bar14)

sum_bar14<- sum(bar14$sequence_length_template)

bar14_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode14") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar15

bar15 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode15")

nrow_bar15 <- nrow(bar15)

sum_bar15 <- sum(bar15$sequence_length_template)

bar15_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode15") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar16

bar16 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode16")

nrow_bar16 <- nrow(bar16)

sum_bar16 <- sum(bar16$sequence_length_template)

bar16_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode16") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar17

bar17 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode17")

nrow_bar17 <- nrow(bar17)

sum_bar17 <- sum(bar17$sequence_length_template)

bar17_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode17") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar18

bar18 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode18")

nrow_bar18<- nrow(bar18)

sum_bar18 <- sum(bar18$sequence_length_template)

bar18_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode18") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar19

bar19 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode19")

nrow_bar19 <- nrow(bar19)

sum_bar19 <- sum(bar19$sequence_length_template)

bar19_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode19") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar20

bar20 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode20")

nrow_bar20 <- nrow(bar20)

sum_bar20 <- sum(bar20$sequence_length_template)

bar20_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode20") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar21

bar21 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode21")

nrow_bar21 <- nrow(bar21)

sum_bar21 <- sum(bar21$sequence_length_template)

bar21_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode21") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar22

bar22 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode22")

nrow_bar22 <- nrow(bar22)

sum_bar22 <- sum(bar22$sequence_length_template)

bar22_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode22") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar23

bar23 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode23")

nrow_bar23 <- nrow(bar23)

sum_bar23 <- sum(bar23$sequence_length_template)

bar23_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode23") %>%
        filter(passes_filtering == TRUE) %>%
        nrow

#bar24

bar24 <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode24")

nrow_bar24 <- nrow(bar24)

sum_bar24 <- sum(bar24$sequence_length_template)

bar24_passes <- run3_sequencing_summary_clean %>%
        filter(barcode_arrangement == "barcode24") %>%
        filter(passes_filtering == TRUE) %>%
        nrow
```



```{r}
###DATFRAME run 3
#create a dataframe to store all this info:

barcode <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24)
reads <- c(nrow_bar1,nrow_bar2,nrow_bar3,nrow_bar4,nrow_bar5,nrow_bar6,nrow_bar7,nrow_bar8,nrow_bar9,nrow_bar10,nrow_bar11,nrow_bar12,nrow_bar13,nrow_bar14,nrow_bar15,nrow_bar16,nrow_bar17,nrow_bar18,nrow_bar19,nrow_bar20,nrow_bar21,nrow_bar21,nrow_bar23,nrow_bar24) #vector containing all the reads per barcode
bases <- c(sum_bar1,sum_bar2,sum_bar3,sum_bar4,sum_bar5,sum_bar6,sum_bar7,sum_bar8,sum_bar9,sum_bar10,sum_bar11,sum_bar12,sum_bar13,sum_bar14,sum_bar15,sum_bar16,sum_bar17,sum_bar18,sum_bar19,sum_bar20,sum_bar21,sum_bar21,sum_bar23,sum_bar24)#vector containing all the bases per barcode
passes <- c(bar1_passes,bar2_passes,bar3_passes,bar4_passes,bar5_passes,bar6_passes,bar7_passes,bar8_passes,bar9_passes,bar10_passes,bar11_passes,bar12_passes,bar13_passes,bar14_passes,bar15_passes,bar16_passes,bar17_passes,bar18_passes,bar19_passes,bar20_passes,bar21_passes,bar22_passes,bar23_passes,bar24_passes) #vector containing all the passed reads per barcode
run <- c(3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3)

run3_metrics_for_model <- data.frame(barcode,reads,bases,passes,run)
print(run3_metrics_for_model)

write.csv(run3_metrics_for_model, "run3_metrics_for_model.csv")

```
