---
title: "extraction experiment 2025 superkingdom and bacterial phyla plots"
output: html_notebook
---

This notebook has the 2025 updated plots for: superkingdom counts and proportion plot, bacterial phyla proportion plot and bacterial phyla heat map for both the loose and stringent dataset.

```{r setup}
library(tidyverse)
library(stringr)
```

```{r}
load("loose_ext_exp_2025")
load("stringent_ext_exp_2025")
```


**Loose filtering**

Summarise how many superkingdoms per extraction method

```{r fig.width = 10, fig.height = 11}

#phylum count to proportions
superkingdom_loose_2025 <- loose_ext_exp_2025%>% 
  mutate(read.length.cat = ifelse(query.length > 5000, "read length >5000", 
                                  ifelse(query.length < 1000, "read length <1000",
                                         "read length 1000-5000"))) %>%
  mutate(read.length.cat = factor(read.length.cat, 
                                  levels = c("read length <1000", "read length 1000-5000", "read length >5000"))) %>%
 group_by(extraction.method, superkingdom, read.length.cat) %>%
  summarise(superkingdom_count = n()) %>%
  ungroup() %>%
  group_by(superkingdom, read.length.cat) %>% #added this line of code on 10.2.25 as the previous code was calculating the proportions incorrectly. I need to ungroup on line 34 and regroup just superkingdom and read.length.cat to make sure we are only getting proportions of the phyla present at a specific read length category and not the proportion of the phyla across all read length categories for a given extraction method
  mutate(prop =prop.table(superkingdom_count)) %>%
  arrange(extraction.method, desc(prop)) 
superkingdom_loose_2025

#prop plot

superkingdom_loose_2025 %>% 
  mutate(superkingdom = replace_na(superkingdom, "Unassigned")) %>%
  ggplot(aes(x = extraction.method, y = prop, fill = superkingdom))   +
    geom_col(position = position_dodge()) +
    geom_text(aes(label = sprintf("%0.2f", prop)), position = position_dodge(width = 0.9), vjust = -0.25, size =3) +
    labs(x="DNA extraction method", y="Proportion", 
        title="Proportional distribution of superkingdoms present per extraction method") +
    scale_fill_brewer(palette = "RdYlBu") + # Change fill & color
    theme(axis.text.x = element_text(angle  = 90, vjust = 0.5, hjust = 1)) +
    facet_wrap(~ superkingdom + read.length.cat, ncol = 3, scales = "free_y")

#count plot
my_colours <- RColorBrewer::brewer.pal(5, "RdYlBu")
superkingdom_loose_2025 %>% 
  mutate(superkingdom = replace_na(superkingdom, "Unassigned")) %>%
  ggplot(aes(x = extraction.method, y = superkingdom_count, fill = superkingdom))   +
    geom_col(position = position_dodge()) +
    #geom_text(aes(label = sprintf("%i", superkingdom_count)), angle = 90, size =3,) +
    geom_text(aes(label = sprintf("%i", superkingdom_count)), position = position_dodge(width = 0.9), vjust = -0.25, size =3) +
    labs(x="DNA extraction method", y="Count", 
        title="Distribution of superkingdoms present per extraction method") +
  scale_fill_manual(values =my_colours) +
   # scale_color_manual(values=c("#d73027","#fdae61","#ffffbf","#abd9e9", "#4575b4")) + # Change fill & color
    theme(axis.text.x = element_text(angle  = 90, vjust = 0.5, hjust = 1)) +
    facet_grid(cols = vars(read.length.cat), rows = vars(superkingdom), scales = "free_y")

```


** Loose filtering, bacterial phyla proportions**

Summarise how many bacterial phyla per extraction method



```{r fig.align="centre", fig.width = 12, fig.height = 15, dpi=300}
#install.packages("RColorBrewer")                   # Install RColorBrewer package
library("RColorBrewer") 
library("ggplot2")
#display.brewer.all(colorblindFriendly = TRUE) gives you codes for all the colour blind friendly colour templates
loose_ext_exp_2025_bac <- loose_ext_exp_2025%>% 
  filter(superkingdom == "Bacteria") %>%
  group_by(extraction.method, phylum) %>%
  distinct(subject.tax.ids) %>% #adding this 26.4.24 to remove multiple hits to the same taxa, inflating the numbers
  summarise(phylum_count = n()) %>%
  mutate(prop =prop.table(phylum_count)) %>%
  ungroup() %>%
  arrange(desc(prop)) %>%
  mutate(phylum = replace_na(phylum, "Unassigned")) %>%
  mutate(phylum = factor(phylum, levels = unique(phylum)))
loose_ext_exp_2025_bac
  
 # mutate(prop =prop.table(phylum_count)) %>%
#  arrange(extraction.method, desc(prop)) %>%
 #   slice(1:10) 
#phyla_prop #pseudomonadota is a synonym for proteobacteria!Bacillota used to be called firmicutes....see https://science.thewire.in/the-sciences/ncbi-taxonomy-prokaryotes-phylum-names-firmicutes-proteobacteria/ for recent (2021) taxonomy changes
# my_colours <- RColorBrewer::brewer.pal(10, "RdYlBu")[1:10]
loose_ext_exp_2025_bac %>% 
 # filter(prop > 0.002) %>% #filter to phyla that are present at least 0.2% in the data
  #mutate(phylum = if_else(prop < 0.002, "Other", phylum)) %>%#if the proporion of the phyla is less than 0.2%, then put all these phyla as 'other'\
  mutate(phylum = if_else(prop < 0.02, "Other", phylum)) %>% #AFTER FILTERING FOR UNIQUE TAXA ID, im now changing the other phyla proportion to 0.02, becuase a lot more will be represented on the graph if i left it at 0.002
  ggplot(aes(x=extraction.method,y=prop, fill=phylum)) +
    geom_col() +
   # ylim(1,0) +
  ylim(0,1) + #26.4.24 flipping this back to 0 to 1 becuase its more interpretable now
    labs(x="DNA extraction method", y="Proportion") +
        #title="Proportional distribution of bacterial phyla present per extraction method") +
     theme(text = element_text(size=25),
    axis.text.x = element_text(angle  = 90, vjust = 1.0, hjust = 1.0)) +
  #scale_fill_brewer(palette = "RdYlBu", direction = 1) + 
scale_fill_manual(values=c("#dd3497","#ffffbf", "#313695", "#abd9e9","#fdae61", "#4575b4","#a50026","#addd8e","#bcbddc", "#fee090" ))
 

#ggsave(file ="bacterial_phyla_all_count_other_212224.png", plot = phyla_prop, width=4, height=4,dpi=300")

ggsave(file="bacterial_phyla_prop_2025_loose.pdf", width=4, height=4) 
```



**loose filtering - heatmap of bacteria phyla**

```{r fig.align="centre", fig.width = 15, fig.height = 18, dpi=300}
library(ggplot2)
packageVersion("ggplot2")
library("RColorBrewer") 
packageVersion("RColorBrewer")

loose_ext_exp_2025 %>%
  filter(superkingdom == "Bacteria") %>%
  group_by(phylum, extraction.method) %>%
  summarise(phylum_count = n()) %>%
  arrange(desc(phylum_count)) %>%
  top_n(10, phylum_count) %>%
ggplot(aes(x = extraction.method, y = phylum, fill = log10(phylum_count))) +
  geom_tile() +
  theme(text = element_text(size=25),
    axis.text.x = element_text(angle  = 90, vjust = 1.0, hjust = 1.0)) +
  scale_fill_distiller(palette = 'YlOrRd', direction = 1) +
  labs(x="DNA extraction method", y="Bacterial phyla")
        #title="Heat map of bacterial phyla present in the core dataset")
```



**Stringent filtering**

Summarise how many superkingdoms per extraction method

```{r fig.width = 10, fig.height = 11}

#phylum count to proportions
superkingdom_stringent_2025 <- stringent_ext_exp_2025%>% 
  mutate(read.length.cat = ifelse(query.length > 5000, "read length >5000", 
                                  ifelse(query.length < 1000, "read length <1000",
                                         "read length 1000-5000"))) %>%
  mutate(read.length.cat = factor(read.length.cat, 
                                  levels = c("read length <1000", "read length 1000-5000", "read length >5000"))) %>%
 group_by(extraction.method, superkingdom, read.length.cat) %>%
   summarise(superkingdom_count = n()) %>%
  ungroup() %>%
  group_by(superkingdom, read.length.cat) %>% 
  mutate(prop =prop.table(superkingdom_count)) %>%
  arrange(extraction.method, desc(prop)) 
superkingdom_stringent_2025

#prop plot

superkingdom_stringent_2025 %>% 
  mutate(superkingdom = replace_na(superkingdom, "Unassigned")) %>%
  ggplot(aes(x = extraction.method, y = prop, fill = superkingdom))   +
    geom_col(position = position_dodge()) +
    geom_text(aes(label = sprintf("%0.2f", prop)), position = position_dodge(width = 0.9), vjust = -0.25, size =3) +
    labs(x="DNA extraction method", y="Proportion", 
        title="Proportional distribution of superkingdoms present per extraction method") +
    scale_fill_brewer(palette = "RdYlBu") + # Change fill & color
    theme(axis.text.x = element_text(angle  = 90, vjust = 0.5, hjust = 1)) +
    facet_wrap(~ superkingdom + read.length.cat, ncol = 3, scales = "free_y")

#count plot
my_colours <- RColorBrewer::brewer.pal(5, "RdYlBu")
superkingdom_stringent_2025 %>% 
  mutate(superkingdom = replace_na(superkingdom, "Unassigned")) %>%
  ggplot(aes(x = extraction.method, y = superkingdom_count, fill = superkingdom))   +
    geom_col(position = position_dodge()) +
    #geom_text(aes(label = sprintf("%i", superkingdom_count)), angle = 90, size =3,) +
    geom_text(aes(label = sprintf("%i", superkingdom_count)), position = position_dodge(width = 0.9), vjust = -0.25, size =3) +
    labs(x="DNA extraction method", y="Count", 
        title="Distribution of superkingdoms present per extraction method") +
  scale_fill_manual(values =my_colours) +
   # scale_color_manual(values=c("#d73027","#fdae61","#ffffbf","#abd9e9", "#4575b4")) + # Change fill & color
    theme(axis.text.x = element_text(angle  = 90, vjust = 0.5, hjust = 1)) +
    facet_grid(cols = vars(read.length.cat), rows = vars(superkingdom), scales = "free_y")

```

***Stringent filtering, bacterial phyla **


Summarise how many bacterial phyla per extraction method



```{r fig.align="centre", fig.width = 12, fig.height = 15, dpi=300}
#install.packages("RColorBrewer")                   # Install RColorBrewer package
library("RColorBrewer") 
library("ggplot2")
#display.brewer.all(colorblindFriendly = TRUE) gives you codes for all the colour blind friendly colour templates
stringent_ext_exp_2025_bac <- stringent_ext_exp_2025%>% 
  filter(superkingdom == "Bacteria") %>%
  group_by(extraction.method, phylum) %>%
  distinct(subject.tax.ids) %>% #adding this 26.4.24 to remove multiple hits to the same taxa, inflating the numbers
  summarise(phylum_count = n()) %>%
  mutate(prop =prop.table(phylum_count)) %>%
  ungroup() %>%
  arrange(desc(prop)) %>%
  mutate(phylum = replace_na(phylum, "Unassigned")) %>%
  mutate(phylum = factor(phylum, levels = unique(phylum)))
#display.brewer.all(colorblindFriendly = TRUE) gives you codes for all the colour blind friendly colour templates
stringent_ext_exp_2025_bac
  
 # mutate(prop =prop.table(phylum_count)) %>%
#  arrange(extraction.method, desc(prop)) %>%
 #   slice(1:10) 
#phyla_prop #pseudomonadota is a synonym for proteobacteria!Bacillota used to be called firmicutes....see https://science.thewire.in/the-sciences/ncbi-taxonomy-prokaryotes-phylum-names-firmicutes-proteobacteria/ for recent (2021) taxonomy changes
# my_colours <- RColorBrewer::brewer.pal(10, "RdYlBu")[1:10]
#display.brewer.all(colorblindFriendly = TRUE) gives you codes for all the colour blind friendly colour templates
stringent_ext_exp_2025_bac %>% 
 # filter(prop > 0.002) %>% #filter to phyla that are present at least 0.2% in the data
  #mutate(phylum = if_else(prop < 0.002, "Other", phylum)) %>%#if the proporion of the phyla is less than 0.2%, then put all these phyla as 'other'\
  mutate(phylum = if_else(prop < 0.02, "Other", phylum)) %>% #AFTER FILTERING FOR UNIQUE TAXA ID, im now changing the other phyla proportion to 0.02, becuase a lot more will be represented on the graph if i left it at 0.002
  ggplot(aes(x=extraction.method,y=prop, fill=phylum)) +
    geom_col() +
   # ylim(1,0) +
  ylim(0,1) + #26.4.24 flipping this back to 0 to 1 becuase its more interpretable now
    labs(x="DNA extraction method", y="Proportion") +
        #title="Proportional distribution of bacterial phyla present per extraction method") +
     theme(text = element_text(size=25),
    axis.text.x = element_text(angle  = 90, vjust = 1.0, hjust = 1.0)) +
  #scale_fill_brewer(palette = "RdYlBu", direction = 1) + 
scale_fill_manual(values=c("#dd3497","#ffffbf", "#313695", "#abd9e9","#fdae61", "#4575b4","#a50026","#addd8e","#bcbddc", "#fee090" ))
 

#ggsave(file ="bacterial_phyla_all_count_other_212224.png", plot = phyla_prop, width=4, height=4,dpi=300")

ggsave(file="bacterial_phyla_prop_2025_stringent.pdf", width=4, height=4) 
```

**stringent filtering - heatmap of bacteria phyla**

```{r fig.align="centre", fig.width = 15, fig.height = 18, dpi=300}
library(ggplot2)
packageVersion("ggplot2")
library("RColorBrewer") 
packageVersion("RColorBrewer")

stringent_ext_exp_2025 %>%
  filter(superkingdom == "Bacteria") %>%
  group_by(phylum, extraction.method) %>%
  summarise(phylum_count = n()) %>%
  arrange(desc(phylum_count)) %>%
  top_n(10, phylum_count) %>%
ggplot(aes(x = extraction.method, y = phylum, fill = log10(phylum_count))) +
  geom_tile() +
  theme(text = element_text(size=25),
    axis.text.x = element_text(angle  = 90, vjust = 1.0, hjust = 1.0)) +
  scale_fill_distiller(palette = 'YlOrRd', direction = 1) +
  labs(x="DNA extraction method", y="Bacterial phyla")
        #title="Heat map of bacterial phyla present in the core dataset")
```
